\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-05-12 paper/main.tex
Added affiliation city and ccs, adjusted space

\author{M M Abid Naziri}
\affiliation{%
  \institution{NC State University, USA}
  %\city{Rocquencourt}
  \country{}
}
\email{mnaziri@ncsu.edu}

\author{Aman Kumar Singh}
\affiliation{%
 \institution{Amrita Vishwa Vidyapeetham, India}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{amanks@am.amrita.edu}

\author{Feiran Qin}
\affiliation{%
 \institution{NC State University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{fqin2@ncsu.edu}

\author{Benjamin Wu}
\affiliation{%
 \institution{Purdue University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{wu2059@purdue.edu}

\author{Saikat Dutta}
\affiliation{%
 \institution{Cornell University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{saikatd@cornell.edu}

\author{Marcelo d'Amorim}
\affiliation{%
 \institution{NC State University, USA}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{}
}
\email{mdamori@ncsu.edu}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% \begin{CCSXML}
%% <ccs2012>
%%  <concept>
%%   <concept_id>00000000.0000000.0000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>500</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>300</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%% </ccs2012>
%% \end{CCSXML}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Deep learning libraries, testing, benchmarking}
%% %% A "teaser" image appears between the author and affiliation
%% %% information and the body of the document, and typically spans the
%% %% page.
%% \begin{teaserfigure}
%%   \includegraphics[width=\textwidth]{sampleteaser}
%%   \caption{Seattle Mariners at Spring Training, 2010.}
%%   \Description{Enjoying the baseball game from the third-base
%%   seats. Ichiro Suzuki preparing to bat.}
%%   \label{fig:teaser}
%% \end{teaserfigure}

@@

\section{Introduction}

@@

%%~\cite{just2014defects4j,smytzek2024tests4py,widyasari2020bugsinpy,kim2021denchmark}
Although many datasets of reproducible bugs have been proposed in the
literature, there is a lack of solutions satisfying the following
criteria:

\begin{enumerate}[leftmargin=0.2in]
\item developers should be able to write test scripts in Python;
\item they should be able to handle nighly builds and specific
  versions of CUDA (\textsection~\ref{sec:challenges});
\item they should be able to integrate fuzzing tools in the framework.
\end{enumerate}

Note that DL libraries are written in Python. Existing datasets of
reproducible bugs exist in Python (e.g.,
BugInPy~\cite{widyasari2020bugsinpy} and
Tests4Py~\cite{smytzek2024tests4py}), but they fail to satisfy the
second or the third requirement. For example, BugsInPy and Tests4Py do
not support artifacts in Docker, which are necessary to modify CUDA
drivers in the guest OS to reproduce specific GPU-related
bugs.\footnote{BugsInPy and Tests4Py use python virtual environments,
e.g., venv and pyenv.} More importantly, a dataset of Deep Learning
Libraries needs to support the integration of new fuzzing tools. The
central purpose of such dataset is to \emph{enable the systematic
evaluation of testing techniques}.

@@

%\Fix{Need to add text regarding differentiating the tool from BugsInPy}

\section{Tool Availability}
\label{sec:tool-availability}
\tname\ is publicly available from the following URL:

\url{https://github.com/ncsu-swat/bugsindlls}

\vspace{0.5ex}\noindent{}The video from this URL demonstrates \tname:

\url{https://www.youtube.com/watch?v=NslNWrULT1c}

\vspace{0.5ex}\noindent{}The archived version at Zenodo is available with this DOI:

\url{https://doi.org/10.5281/zenodo.15064163}\\

% \Fix{Upload to YouTube with voiceover and add link here, archive 
% the tool at zenodo}

\section{Objects and Methods}

@@

\section*{Acknowledgements}
This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.

>>>>

\author{M M Abid Naziri}
\affiliation{%
  \institution{NC State University, Raleigh, USA}
  % \city{Raleigh}
  % \country{USA}
  \country{}
}
\email{mnaziri@ncsu.edu}

\author{Aman Kumar Singh}
\affiliation{%
 \institution{Amrita Vishwa Vidyapeetham, Coimbatore, India}
%  \city{Coimbatore}
%  \country{India}
 \country{}
}
\email{amanks@am.amrita.edu}

\author{Feiran Qin}
\affiliation{%
\institution{NC State University, Raleigh, USA}
% \city{Raleigh}
% \country{USA}
\country{}
}
\email{fqin2@ncsu.edu}

\author{Benjamin Wu}
\affiliation{%
 \institution{Purdue University, West Lafayette, USA}
%  \city{West Lafayette}
%  \country{USA}
 \country{}
}
\email{wu2059@purdue.edu}

\author{Saikat Dutta}
\affiliation{%
 \institution{Cornell University, Ithaca, USA}
%  \city{Ithaca}
%  \country{USA}
 \country{}
}
\email{saikatd@cornell.edu}

\author{Marcelo d'Amorim}
\affiliation{%
\institution{NC State University, Raleigh, USA}
% \city{Raleigh}
% \country{USA}
\country{}
}
\email{mdamori@ncsu.edu}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% \begin{CCSXML}
%% <ccs2012>
%%  <concept>
%%   <concept_id>00000000.0000000.0000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>500</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>300</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>00000000.00000000.00000000</concept_id>
%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%% </ccs2012>
%% \end{CCSXML}
\vspace{-0.3cm}
\begin{CCSXML}
  <ccs2012>
    <concept>
        <concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
        <concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
        <concept_significance>500</concept_significance>
        </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software testing and debugging}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\vspace{-0.3cm}
\keywords{Deep learning libraries, testing, benchmarking}
%% %% A "teaser" image appears between the author and affiliation
%% %% information and the body of the document, and typically spans the
%% %% page.
%% \begin{teaserfigure}
%%   \includegraphics[width=\textwidth]{sampleteaser}
%%   \caption{Seattle Mariners at Spring Training, 2010.}
%%   \Description{Enjoying the baseball game from the third-base
%%   seats. Ichiro Suzuki preparing to bat.}
%%   \label{fig:teaser}
%% \end{teaserfigure}

@@

\vspace{-2ex}
\section{Introduction}

@@

%%~\cite{just2014defects4j,smytzek2024tests4py,widyasari2020bugsinpy,kim2021denchmark}
Although many datasets of reproducible bugs have been proposed in the
literature, there is a lack of solutions satisfying the following
criteria:
% \vspace{-2ex}
\begin{enumerate}[leftmargin=0.2in,topsep=0pt]
\item ability to write test scripts in Python;
\item handlin nightly builds and specific
  CUDA versions (\textsection~\ref{sec:challenges});
\item ability to integrate fuzzing tools in the framework.
\end{enumerate}  
% \vspace{-2ex}
Note that DL libraries are written in Python. Existing datasets of
reproducible bugs exist in Python (e.g.,
BugInPy~\cite{widyasari2020bugsinpy} and
Tests4Py~\cite{smytzek2024tests4py}), but they fail to satisfy the
second or the third requirement. For example, BugsInPy and Tests4Py do
not support artifacts in Docker, which are necessary to modify CUDA
drivers in the guest OS to reproduce specific GPU-related
bugs.\footnote{BugsInPy and Tests4Py use python virtual environments,
e.g., venv and pyenv.} More importantly, a dataset of Deep Learning
Libraries needs to support the integration of new fuzzing tools. The
central purpose of such dataset is to \emph{enable the systematic
evaluation of testing techniques}.

@@

%\Fix{Need to add text regarding differentiating the tool from BugsInPy}
\vspace{-0.29cm}
\section{Tool Availability}
\label{sec:tool-availability}
\tname\ is publicly available from the following URL:
\url{https://github.com/ncsu-swat/bugsindlls}

\noindent{}The video from this URL demonstrates \tname:
\url{https://www.youtube.com/watch?v=NslNWrULT1c}

% \vspace{0.5ex}\noindent{}The archived version at Zenodo is available with this DOI:

% \url{https://doi.org/10.5281/zenodo.15064163}\\

% \Fix{Upload to YouTube with voiceover and add link here, archive 
% the tool at zenodo}
\vspace{-0.2cm}
\section{Objects and Methods}

@@

\vspace{-1ex}
\section*{Acknowledgements}
This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.
